\documentclass[oneside, notitlepage, twocolumn]{scrartcl}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage[acronym, automake, nopostdot, nomain, numberedsection, section]{glossaries}
\usepackage{biblatex}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{url}
\usepackage{xcolor}
\usepackage{xspace}

\newcommand{\tableheadline}[1]{\textbf{#1}}
\newcommand{\draft}[1]{\textcolor{red}{\textit{#1}}}
\newcommand{\eg}{e.\,g.\xspace}

\renewcommand\cellalign{lt}

\setlength{\parskip}{1mm}
\setlength{\parindent}{0pt}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{2pt plus 2pt minus 2pt}

\title{\LARGE Testing Vision-Based Control Systems Using Learnable Evolutionary Algorithms}
\subtitle{Summary}
\author{Stefan Huber}

\addbibresource{references21.bib}

\makeglossaries%
\newacronym{nsgaii}{NSGA-II}{Non-dominated Sorting Genetic Algorithm-II}
\newacronym{aeb}{AEB}{Automated Emergency Breaking}
\newacronym{adas}{ADAS}{Advanced Driving Assistance System}

\begin{document}

\maketitle

\section{Summary}
The paper discusses finding critical test cases for simulation-based testing of vision-based control systems like \glspl{adas} based on evolutionary search algorithms.
\draft{The approach is explained using only their results on \gls{aeb}.}\par
To improve the effectiveness of evolutionary multi-objective search algorithms the approach combines them with decision trees.
Decision trees are repeatedly build after a few iterations of the evolutionary search algorithm.
Each node of a tree represents a population of test scenarios fulfilling all the constraints annotated on the edges of the path from the root to this node.
Every node has values (in \%) which describe the certainty finding critical and non-critical test cases.
If a node has more than 95\% criticality it is marked as critical region.
The constraints of the edges on the path from the root to the node characterize the test scenarios.\par
The next iterations of the evolutionary search algorithm concentrate on non-critical regions to find more critical regions by identifying subregions.\par
%\draft{Every \gls{adas} is described as a tuple \((S, O, I, D, C)\) where \(S\) is the set of immobile objects, \(O\) is the set of mobile objects, \(I\) is the set of initial states of the mobile objects, \(D\) is the domain where the variables are in and \(C\) is a set of boolean constraints to \(S\) and \(I\).}

\section{Critical Content}
According to the paper ten \glspl{adas} were studied during the research but the only \gls{adas} described is \gls{aeb}.
The paper mentions neither the results nor any analysis (not even the names) of the other nine \glspl{adas}.\\
In section 4.1 the paper lists many parameters and configurations, but some of their chosen values are not specified or only given a few pages later in section 5.3 (\eg{} the mutation rate).
In section 4.1 the mutation rate is only described as ``a probability''.\\
The title suggests that the research discusses multiple evolutionary search-based algorithms but the only one referred to is \gls{nsgaii}.\\
The section ``Benefits from a practitioner's perspective'' deals with exactly three people who are employees of the same company which is exactly the company supporting the research itself.
Additionally one of these three people is connected to the research team.\\
As a conclusion I do not like the paper and if I use the approach proposed by this paper I would at most use it for testing \gls{aeb}.
\draft{%
    \begin{itemize}
        \item (Assumption pedestrian linear trajectory)
        \item They say they studied ten \glspl{adas} but only mention the \gls{aeb} (Section 4.1). Since cooperation with industry?
        \item They do not mention the mutation rate or whether they fixed it. (Section 4.1). They mention a mutation rate only for \gls{aeb} in section 5.3.
        \item In section 5.3 they mention they ``could tune the parameters'' but they do neither say how nor anything else about that.
        \item The title mentions ``Evolutionary Algorithms'' but they use only \gls{nsgaii}.
        \item (Results of RQ2 are not scientific.)
        \item ``Benefits from a practitioner's perspective'' with three people where one is already connected to the research itself\ldots
    \end{itemize}
}

\section{Critical Questions}
\begin{enumerate}
    \item Did the other \glspl{adas} perform similar to \gls{aeb}?
\end{enumerate}

\printglossary[type=\acronymtype, title=List of Abbreviations]

\section{References}
\begingroup
\renewcommand{\section}[2]{}%
\nocite{*}
\printbibliography%
\endgroup

\twocolumn[{%
\section{Related Work}
% At least 4 not explicitly mentioned other papers
% How did I find it?
% Why did I choose it?
\begin{tabularx}{\textwidth}{lXX}
    \tableheadline{Reference} & \tableheadline{Search strategy} & \tableheadline{Why chosen?}\\
    \midrule
    cite & strategy & reasons\\
    \midrule
    cite & strategy & reasons\\
    \midrule
    cite & strategy & reasons\\
    \midrule
    cite & strategy & reasons\\
\end{tabularx}
}]

\end{document}
